Unsupervised Detection and Tracking of Arbitrary Objects with Dependent Dirichlet Process Mixtures

### 2012-02-08 ltx/paper_short.tex
I really need to clean up this repo. sorry. the  main tex file is paper_short_2.tex

We define the task of automated detection and tracking of arbitrary objects in videos to consist of three actions: determining the spatiotemporal regions of a video that constitute objects (``extraction''), finding the positions and/or shapes of distinct objects (``localization''), and maintaining the identities of the detected objects over time (``tracking''). An ability to carry out these tasks in an automated manner is useful for many fields that make use of video data, including robotics, video surveillance, time-lapse microscopy, and video summarization. Algorithms able to be applied to a variety of objects and video types are particularly desirable. This paper introduces a new framework involving the use of dependent Dirichlet process mixture models. This framework provides a foundation for a class of unsupervised algorithms that can detect and track arbitrary objects in a wide range of videos.

Research on methods for general detection and tracking of objects has focused on one of either extraction, localization, or tracking. Integrating all three tasks in a system for multiple arbitrary objects and diverse video types was not often a primary focus. Accomplishing the three tasks in a cohesive manner has been pursued more recently and has produced algorithms that can, in a fully automated way, accomplish unsupervised detection and tracking---or in short, that can determine the spatiotemporal region of a video occupied by each distinct object. An example of general detection and tracking is called ``blob tracking'', which typically refers to methods that perform extraction and localization of objects in each frame independently. Tracking involves finding blobs with similar locations and appearances over time. The main blob tracking challenges are the difficulty of segmenting neighboring or occluding objects in a given frame \cite{zhao2004tracking} and preventing multiple tracked blobs from merging into a single object \cite{vermaak_2003}. These difficulties stem from performing detection via segmentation on individual frames.

>>>>

We define the task of automated detection and tracking of arbitrary objects in videos to be: extraction, localization, and tracking. Extraction is the task of determining the spatiotemporal regions of a video that constitute objects, localization is the task of finding the positions and/or shapes of distinct objects, and tracking is the task of maintaining the identities of the detected objects over time. An ability to carry out these tasks in an automated manner is useful for many fields that make use of video data, including robotics, video surveillance, time-lapse microscopy, and video summarization. Algorithms able to be applied to a variety of objects and video types are particularly desirable. This paper introduces a new framework involving the use of dependent Dirichlet process mixture models. This framework provides a foundation for a class of unsupervised algorithms that can detect and track arbitrary objects in a wide range of videos.

Research on methods for general detection and tracking of objects has focused on one of either extraction, localization, or tracking. Integrating all three tasks in a system for multiple arbitrary objects and diverse video types was not often a primary focus. Accomplishing the three tasks in a cohesive manner has been pursued more recently and has produced algorithms that can, in a fully automated way, accomplish unsupervised detection and tracking---or in short, that can determine the spatiotemporal region of a video occupied by distinct objects. An example of general detection and tracking is called ``blob tracking'', which typically refers to methods that perform extraction and localization of objects in each frame independently. Tracking involves finding blobs with similar locations and appearances over time. The main blob tracking challenges are the difficulty of segmenting neighboring or occluding objects in a given frame \cite{zhao2004tracking} and preventing multiple tracked blobs from merging into a single object \cite{vermaak_2003}. These difficulties stem from performing detection via segmentation on individual frames.
